Deep Probabilistic Models for Camera Geo-Calibration

### 2018-09-17 chapters/discussion/discussion.tex
minor change

In \chapref{mcmc}, we proposed a flexible model to compute the
probability over all geo-calibration parameters. In the high
dimensional space of geo-calibration parameters, we defined an score
function for every point in that space, to measure how well the
geo-calibration parameters match the content of the input image. The
score function is defined as a weighted summation of a series of
constraint functions, and is proportional to the probability density
function of the distribution. Since xxx is computationally
intractable, in order to xxx, we approximated the probability
density function using MCMC method.

In \chapref{fasthorizon}, we focused on constraint function for the
camera pose. Assuming the focal length is known, the camera roll and
pitch angle can be derived from the horizon line position. Our
algorithm identifies the horizon line from an input image that
satisfied the Manhattan world assumption.
Compared to most previous work which applies a bottom-up approach by
fitting the horizon line from the vanishing points, we proposed a
novel horizon-first approach to identify the horizon line.
First we trained a CNN to estimate the distribution of the horizon
line. Then we sample horizon line candidates from the horizon line
distribution. For each horizon candidate, we find the possible
vanishing points on it. Compared to previous work which searches for 
vanishing points on image frame, our method accelerate the searching
process by carrying it out in the 1D space. The probability of the
horizon candidate to be the real horizon line is measured by how many
and good vanishing points found on it.

>>>>

In \chapref{mcmc}, we proposed a flexible model to compute the
probability over all geo-calibration parameters. In the high
dimensional space of geo-calibration parameters, we defined a score
function for every point, to measure how well the
geo-calibration parameters match the content of the input image.
The score function is a weighted summation of a series of
constraint functions. It is proportional to the probability density
function of the distribution. Since the analytic solution to the
integral of the score function does not exist, we approximated the
probability density function using MCMC method. Our model is flexible
to any constraint function for geo-calibration parameters. We also
demonstrated in our experiment that more accurate predictions can be
obtained if the score function consists of more constraints.

In \chapref{fasthorizon}, we focused on developing constraint function
for the camera pose. Assuming the focal length is known, the camera
roll and pitch angle can be derived from the horizon line position.
Our algorithm identifies the horizon line from the input image
satisfying the Manhattan world assumption. Compared to the previous
work, which applies a bottom-up approach where the horizon line is
estimated after the vanishing point identification, we proposed a
novel horizon-first approach where finding horizon line candidates is
prior to identifying vanishing points.  As the first step, we trained
a CNN to estimate the probability distribution over the horizon line.
Then we sample horizon line candidates from the distribution. For each
horizon candidate, we detect likely vanishing points on it. Compared
to previous work which searches for vanishing points on the 2D image
frame, our method is able to accelerate the searching process by
reducing the searching space to 1D. The probability of the horizon
line is measured by how convincing are the vanishing points found on
it.
